Article Title

### 2013-08-10 sections/Introduction.tex
minor changes
minor

Pearson correlations between the spiking activity of pairs of neurons, or simply \emph{neural correlations}, are among the most familiar descriptive statistics of neural population activity \citep{Cohen:2011}.  For example, \emph{noise correlations}, \emph{i.e.}~the correlations of stimulus response variability between pairs of neurons, have been of particular interest.  Noise correlations can have profound theoretical implications for stimulus coding \citep{Zohary:1994,Abbott:1999,Averbeck:2006,Berens:2011}, and have been interpreted to indicate detailed and specific functional organization. Such interpretation is supported by a series of discoveries of nontrivial relationships between neural correlations and other aspects of circuit organization such as the physical distance separating the neurons, their synaptic connectivity and stimulus tuning similarity, cortical layer specificity, cell-type specificity, progressive changes in development and in learning, changes due to sensory stimulation and global brain states, and others \citep{Kohn:2005,Smith:2008,Kohn:2009,Goard:2009,Golshani:2009,Renart:2010,Ecker:2010,Ko:2011,Smith:2013,Denman:2013}.

>>>>

Pearson correlations between the spiking activity of pairs of neurons, or simply \emph{neural correlations}, are among the most familiar descriptive statistics of neural population activity \citep{Averbeck:2006,Zohary:1994,Kohn:2005,Bair:2001,Renart:2010}.  For example, \emph{noise correlations}, \emph{i.e.}~the correlations of stimulus response variability between pairs of neurons, have been of particular interest.  Noise correlations can have profound theoretical implications for stimulus coding \citep{Zohary:1994,Abbott:1999,Averbeck:2006,Berens:2011,Ecker:2011}, and have been interpreted to indicate detailed and specific functional organization. Such interpretation is supported by a series of discoveries of nontrivial relationships between neural correlations and other aspects of circuit organization such as the physical distance separating the neurons \citep{Smith:2008,Denman:2013}, their synaptic connectivity and stimulus tuning similarity \citep{Kohn:2005,Ko:2011}, cortical layer specificity \citep{Hansen:2012,Smith:2013}, cell-type specificity (?), progressive changes in development and in learning \citep{Golshani:2009}, changes due to sensory stimulation and global brain states \citep{Goard:2009,Kohn:2009,Ecker:2010,Renart:2010}, and others.

### 2013-08-10 sections/Theory.tex
minor

Regularization requires making the following three choices: 
\begin{enumerate}[  1. ]
\item define a set of low-dimensional target estimates
\item given the data, select the optimal target estimate from the set 
\item given the data, select the optimal amount of biasing toward the target estimate
\end{enumerate}
The first choice, the selection of the general form of target estimates, must be made \emph{a priori}.  Curiously, \emph{some} improvement can be produced with an arbitrary target estimate as long as its variance is lower than that of the unbiased estimator.  The perplexing fact that estimates can be improved by biasing toward an arbitrary less variable target is known as \emph{Stein's paradox} \citep{Efron:1977}.

\subsection{Probabilistic framework}

Let $x_i \in \mathcal X, i=1\ldots,x_n$ denote a sample of consequtive observations of population activity of $p$ neurons in time bins $i$.  
The activity of each neuron is the real-valued firing rate \TODO{Need to define rate more precisely}, thus  $\mathcal X = \mathbb R^{p\times 1}$.  
We assume that observations are drawn from some true cumulative probability distribution $F: \mathcal X \mapsto R$. Then let $\hat F_n$ denote the empirical distribution function obtained from the observed sample, which itself is a random variable.
\begin{equation}
\hat F_n(x) = \frac 1 n \sum\limits_{i=1}^n \mathbf{1}(x \ge x_i)
\end{equation}
where $\mathbf 1(x \ge x_i)$ is the indicator function which equals 1 when all elements of $x$ are greater than the corresponding elements of $x_i$ and 0 otherwise. \TODO{KJ: Are you using cumulative distributions to avoid binning? DY: Yes. Many theorems such as Glivenko-Catelli Theorem and Skorohod's Representation are proven using  cumulative representation. The empirical distribution is nearly always represented in its cumulative form. Expressing convergence is requires binning or using cumulative; the latter is simpler.}

@@

\begin{figure}
\centering
\includegraphics[width=0.6\textwidth]{figures/Figure2.pdf}
\caption{
%\textbf{Figure 2.}{
Gaussian Graphical models corresponding to the low-dimensional targets of the four regularization schemes used in the paper.
\textbf{A}: A diagonal matrix corresponds to a Gaussian graphical model with no dependencies. 
\textbf{B}: In factor analysis, observed nodes are assumed to be influenced by several latent units (``factors") but are otherwise independent. 
\textbf{C}: In the Gaussian graphical model (also known as the Gaussian Markov Field), correlations arise from sparse pairwise linear interactions between visible units. 
\textbf{D}: In the Gaussian graphical model with latent units, correlations arise  between pairs of nodes 
}\label{fig:02}
%}
\end{figure}

>>>>

A regularized estimate requires the following three choices: 
\begin{enumerate}[  1. ]
\item define a set of low-dimensional target estimates
\item given the data, select the optimal target estimate from the set 
\item given the data, select the optimal amount of biasing toward the target estimate
\end{enumerate}
The first choice, the selection of the general form of target estimates, must be made \emph{a priori}.  Curiously, \emph{some} improvement can be produced with an arbitrary target estimate as long as its variance is lower than that of the unbiased estimator.  The perplexing fact that estimates can be improved by biasing toward an arbitrary less variable target is known as \emph{Stein's paradox} \citep{Efron:1977}.

\subsection{Probabilistic framework}
\TODO{This section is not strictly necessary. It helps relate probabilistic models to our approach, which does not rely on an explicity probabilistic model.}
Let $x_i \in \mathcal X, i=1\ldots,x_n$ denote a sample of consequtive observations of population activity of $p$ neurons in time bins $i$.  
The activity of each neuron is the real-valued firing rate \TODO{Need to define rate more precisely}, thus  $\mathcal X = \mathbb R^{p\times 1}$.  
We assume that observations are drawn from some true cumulative probability distribution $F: \mathcal X \mapsto R$. Then let $\hat F_n$ denote the empirical distribution function obtained from the observed sample, which itself is a random variable.
\begin{equation}
\hat F_n(x) = \frac 1 n \sum\limits_{i=1}^n \mathbf{1}(x \ge x_i)
\end{equation}
where $\mathbf 1(x \ge x_i)$ is the indicator function which equals 1 when all elements of $x$ are greater than the corresponding elements of $x_i$ and 0 otherwise. \TODO{KJ: Are you using cumulative distributions to avoid binning? DY: Yes. Many theorems such as Glivenko-Catelli Theorem and Skorohod's Representation are proven using  cumulative representation. The empirical distribution is nearly always represented in its cumulative form. Expressing convergence is requires binning or using cumulative; the latter is simpler.}

@@

\begin{figure}
\centering
\includegraphics[width=0.6\textwidth]{figures/Figure2.pdf}
\caption{
%\textbf{Figure 2.}{
Graphical models corresponding to the low-dimensional targets of the four regularization schemes used in the paper.
\textbf{A}: A diagonal matrix corresponds to a Gaussian graphical model with no dependencies. 
\textbf{B}: In factor analysis, observed nodes are assumed to be influenced by several latent units (``factors") but are otherwise independent. 
\textbf{C}: In the Gaussian graphical model (also known as the Gaussian Markov Field), correlations arise from sparse pairwise linear interactions between visible units. 
\textbf{D}: In the Gaussian graphical model with latent units, correlations arise  between pairs of nodes 
}\label{fig:02}
%}
\end{figure}
